Comparison of particle trajectories and collision operators for collisional transport in nonaxisymmetric plasmas

### 2014-02-05 doc/sfincsPaper/sfincsPaper.tex
Added DKES and Simakov-Helander benchmark to figures 4-5, along with associated descriptive text, to sfincs paper.

%\documentclass{amsart}
%\documentclass[aip,graphicx]{revtex4-1}
\documentclass[12pt]{revtex4}
\usepackage{latexsym, color, graphicx, comment}
\usepackage{amssymb}
\usepackage{amsmath}

@@

\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\vect}[1]{\mbox{\boldmath $#1$}}
\newcommand{\erf}{\mathrm{erf}}
\newcommand{\PS}{Pfirsch-Schl\"{u}ter~}
\newcommand{\ExB}{\vect{E}\times\vect{B}}
\newcommand{\Cnl}{C_{\mathrm{nl}a}}
\newcommand{\vma}{\vect{v}_{\mathrm{m}a}}
\newcommand{\vm}{\vect{v}_{\mathrm{m}}}
\newcommand{\vda}{\vect{v}_{\mathrm{d}a}}
\newcommand{\vE}{\vect{v}_{E}}
\newcommand{\vdao}{\vect{v}_{\mathrm{d}a0}}
\newcommand{\vdo}{\vect{v}_{\mathrm{d}0}}
\newcommand{\vEo}{\vect{v}_{E0}}
\newcommand{\vpar}{v_{||}}
\newcommand{\vperp}{v_{\bot}}
\newcommand{\rhop}{\rho_{\theta}}
\newcommand{\rT}{r_{T}}
\newcommand{\vi}{v_{\mathrm{i}}}
\newcommand{\me}{m_{\mathrm{e}}}
\newcommand{\mi}{m_{\mathrm{i}}}
\newcommand{\Ti}{T_{\mathrm{i}}}
\newcommand{\rTi}{r_{T\mathrm{i}}}
\newcommand{\rTe}{r_{T\mathrm{e}}}
\newcommand{\reta}{r_{\eta}}
\newcommand{\rn}{r_{n}}
\newcommand{\rperp}{r_\bot}
\newcommand{\fM}{f_{\mathrm{M}}}
\newcommand{\fMa}{f_{\mathrm{M}a}}
\newcommand{\fMi}{f_{\mathrm{M}i}}
\newcommand{\fMe}{f_{\mathrm{Me}}}
\newcommand{\fe}{f_{\mathrm{e}}}
\newcommand{\Te}{T_{\mathrm{e}}}
\newcommand{\vth}{v_{\mathrm{th}}}
\newcommand{\nuii}{\nu_{\mathrm{ii}}}
\newcommand{\nuPrime}{\hat{\nu}}
\newcommand{\gradpar}{\nabla_{||}}
\newcommand{\kpar}{k_{||}}
\newcommand{\psia}{\psi_0}
\newcommand{\psiaHat}{\hat{\psi}_0}
\newcommand{\todo}[1]{\textcolor{red}{To do: #1}}
\newcommand{\changed}[1]{\textcolor{green}{#1}}
\newcommand{\sgn}{\mathrm{sgn}}
\newcommand{\Erres}{E_r^{\mathrm{res}}}
\newcommand{\Bpol}{B_{\mathrm{pol}}}
\newcommand{\Sap}{S_{a\mathrm{p}}}
\newcommand{\Sah}{S_{a\mathrm{h}}}

@@

\author{M Landreman}
\email[]{mattland@umd.edu}
%\homepage[]{Your web page}
%\thanks{}
\affiliation{Institute for Research in Electronics and Applied Physics, University of Maryland, College Park, MD, 20742, USA}
\affiliation{Plasma Science and Fusion Center, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA}
\author{H M Smith}
\author{P Helander}
\affiliation{Max-Planck-Institut f\"{u}r Plasmaphysik, 17491 Greifswald, Germany}

@@

When the pure pitch-angle scattering collision operator 
and DKES trajectories are chosen, the kinetic equation
solved in SFINCS becomes identical to the one solved in the DKES code \cite{DKES1, DKES2}.
In this case, it was verified that the two codes agreed for all elements of the transport
matrix.

@@

\begin{figure}[h!]
% Figure generated using m20131208_01_plotSFINCSFortranAndMatlabNuScansForPaper.m
% High collisionality runs done in matlab, with data in
% m20130226_04_SFINCS_2013-02-26_21-21_good
% Low collisionality runs done in fortran on edison.
% *********************************
% Old version of figure:
% Figure generated using m20131130_01_plotSFINCSCollisionOperatorComparisonForPaper.m
% Data files:
% m20131117_04_sfincs_w7x_2013-11-26_02-27_nuPrimeScan_nuPrime0_01to100
% m20130226_04_SFINCS_2013-02-26_21-21_good
% W7X run was on edison in /global/scratch2/sd/landrema/20131123-01-sfincs/20131125-02-nuPrimeScan0_01to100
% *********************************
\includegraphics{m20131208_01_plotSFINCSFortranAndMatlabNuScansForPaper_LHD.eps}
%\includegraphics{m20131130_01_plotSFINCSCollisionOperatorComparisonForPaper_LHD.eps}
\caption{(Color online) Comparison of collision operators for LHD standard geometry at $E_r=0$.
The ion transport matrix elements (defined in (\ref{eq:matrix})) are plotted as functions
of the collisionality (\ref{eq:nuPrime}).
\label{fig:collisionComparison_LHD}}
\end{figure}

\begin{figure}[h!]
% Figure generated using m20131208_01_plotSFINCSFortranAndMatlabNuScansForPaper.m
% High collisionality runs done in matlab, with data in
% m20131117_04_sfincs_w7x_2013-11-26_02-27_nuPrimeScan_nuPrime0_01to100
% Low collisionality runs done in fortran on edison.
% *********************************
% Old version of figure:
% Figure generated using m20131130_01_plotSFINCSCollisionOperatorComparisonForPaper.m
% Data files:
% m20131117_04_sfincs_w7x_2013-11-26_02-27_nuPrimeScan_nuPrime0_01to100
% m20130226_04_SFINCS_2013-02-26_21-21_good
% W7X run was on edison in /global/scratch2/sd/landrema/20131123-01-sfincs/20131125-02-nuPrimeScan0_01to100
% *********************************
\includegraphics{m20131208_01_plotSFINCSFortranAndMatlabNuScansForPaper_W7X.eps}
%\includegraphics{m20131130_01_plotSFINCSCollisionOperatorComparisonForPaper_W7X.eps}
\caption{(Color online) Comparison of collision operators for W7-X standard geometry at $E_r=0$.
The ion transport matrix elements (defined in (\ref{eq:matrix})) are plotted as functions
of the collisionality (\ref{eq:nuPrime}).
\label{fig:collisionComparison_W7X}}
\end{figure}

@@

\section{Ion transport matrix at high collisionality}
From the model presented in Ref.~\cite{AndreiPer2009} we can derive expressions for $L_{jk}$ of Eq.~(\ref{eq:matrix}) in the Pfirsch-Schl{\"u}ter regime. 
The coefficients then depend on the function $u$ given by the solution to Eq.~(8) in Ref.~\cite{AndreiPer2009}, which is proportional to the parallel current divided by $B$. 
All coefficients but $L_{33}$ are straightforwardly obtained from Eqs.~(14), (18) and (26) in Ref.~\cite{AndreiPer2009} for the radial ion heat flux, the parallel ion flow and the radial current respectively, by %properly choosing 
suitable choices of 
the thermodynamic forces in the right-hand-side of Eq.~(\ref{eq:matrix}) for different solves and using the symmetry of the transport matrix.
To find the parallel conductivity coefficient $L_{33}$ we substitute the pressure anisotropy, given by Eq.~(20) in Ref.~\cite{AndreiPer2009}, into Eq.~(\ref{ParallelMomentum}) (of this paper) 
in the absence of radial gradients (i.e. when $E_{||}$ is the only thermodynamic force present). $L_{33}$ is then found from the flow $\left< V_\| B \right>$.

Expressions for the matrix coefficients in the Pfirsch-Schl{\"u}ter regime are summarized in Eqs.~(\ref{eq:LPSregime})-(\ref{eq:PSregimeFunctions}). 
Note that the constants in the function ${K}_2 \left(\psi\right)$ in $L_{23}$ have been modified from their values in ${K}_{2}^{\mathrm{Simakov}} \left(\psi\right)$ obtained from Ref.~\cite{AndreiPer2009}, by a more precise solution to the Spitzer problem.

%\begin{equation}
%\begin{array}{c}
\begin{align}
\begin{split}
L_{11} & = 
 0.96 \cdot 2^{1/2} \cdot  \frac{3}{4}  \frac{\left(G + \iota I\right)^2}{ \iota^2 G^2} 
 {G}_1 \left(\psi\right) \frac{1}{\nu'},\\
 %%
L_{12} & = L_{21} =  0.96 \cdot 2^{1/2} \frac{\left({G} + \iota {I}\right)^2}{ \iota^2 {G}^2} \left[ 3.245 \, {G}_1 \left(\psi\right) + 0.085 \, {G}_2 \left(\psi\right)  \right] \frac{1}{\nu'}, \\
%% 
L_{13} & = L_{31}  = \frac{\left\langle {u} {B}^2  \right\rangle}{{G} \iota} - \frac{\left\langle {B}^2\right\rangle}{{G} \iota} {K}_1\left(\psi\right), \\
%%
L_{22} & = 2^{1/2} \cdot  \frac{8}{5} \frac{1}{\iota^2 {G}^2} B_0^2 {H} \left(\psi\right) \, \nu', \\
	%\textcolor{red}{+ \left( \,0.96 \cdot 2^{1/2} \cdot \frac{5}{2} \frac{\left({G} + \iota {I}\right)^2}{ \iota^2 {G}^2} \left[ 3.245 {G}_1 \left(\psi\right) + 0.085 {G}_2 \left(\psi\right)  \right] \frac{1}{\nu'}\right)}, \\
	%%
L_{23} & = L_{32} = \frac{1}{\iota {G}} \left[\frac{5}{2} \left\langle {u} {B}^2  \right\rangle - \frac{5}{2} {K}_1\left(\psi\right) \left\langle {B}^2\right\rangle + {K}_2\left(\psi\right) \left\langle {B}^2\right\rangle\right], \\
%%
L_{33} & = \frac{1}{3 \cdot 0.96 \cdot 2^{1/2}} \frac{1}{\left({G} + \iota {I}\right)^2} \frac{\left\langle {B}^2\right\rangle^2}{\left\langle \left( {\nabla}_\| {B}\right)^2\right\rangle} \, \nu',	
%\end{array}
\label{eq:LPSregime}
\end{split}
\end{align}
%\end{equation}
%where
\begin{align}
\begin{split}
& {G}_1 \left(\psi\right) %& 
= \frac{\left\langle \left( {\nabla}_\| \ln {B}\right)  {\nabla}_\| \left({u} {B}^2\right)\right\rangle^2}{\left\langle \left( {\nabla}_\| {B}\right)^2\right\rangle} -
 \left\langle \left[\frac{ {\nabla}_\| \left({u} {B}^2\right)}{{B}}\right]^2\right\rangle,  \\
 %%
& {G}_2 \left(\psi\right) %& 
 = \left\langle {u} \left({\nabla}_\| \ln {B}\right) {\nabla}_\| \left({u} {B}^2\right) \right\rangle
 - \frac{\left\langle \left( {\nabla}_\| \ln {B}\right)  {\nabla}_\| \left({u} {B}^2\right)\right\rangle
 \left\langle {u} \left( {\nabla}_\| {B}\right)^2\right\rangle}{\left\langle \left( {\nabla}_\| {B}\right)^2\right\rangle},  \\
 %%
& {K}_1 \left(\psi\right) %& 
 = \frac{\left\langle \left( {\nabla}_\| \ln {B}\right)  {\nabla}_\| \left({u} {B}^2\right)\right\rangle}{2 \left\langle \left( {\nabla}_\| {B}\right)^2\right\rangle}, \\
 %%
& {K}_2 \left(\psi\right) %& 
 = 1.97213 \frac{\left\langle {u} {B}^2  \right\rangle}{\left\langle {B}^2  \right\rangle} - 1.03287 \cdot 2 {K}_1 \left(\psi\right)
 + 0.09361 \frac{
 \left\langle {u} \left( {\nabla}_\| {B}\right)^2\right\rangle}{\left\langle \left( {\nabla}_\| {B}\right)^2\right\rangle}, \\
 %%
&  {K}_{2}^{\mathrm{Simakov}} \left(\psi\right) %& 
  = 1.77 \frac{\left\langle {u} {B}^2  \right\rangle}{\left\langle {B}^2  \right\rangle} - 0.91 \cdot 2 {K}_1 \left(\psi\right)
 + 0.05 \frac{
 \left\langle {u} \left( {\nabla}_\| {B}\right)^2\right\rangle}{\left\langle \left( {\nabla}_\| {B}\right)^2\right\rangle}, \\
 %%
& {H} \left(\psi\right) %& 
 = \frac{\left\langle {u} {B}^2  \right\rangle^2}{\left\langle {B}^2  \right\rangle} - \left\langle {u}^2 {B}^2  \right\rangle.
\label{eq:PSregimeFunctions}
\end{split}
\end{align}

>>>>

%\documentclass{amsart}
%\documentclass[aip,graphicx]{revtex4-1}
\documentclass[12pt,superscriptaddress]{revtex4}
\usepackage{latexsym, color, graphicx, comment}
\usepackage{amssymb}
\usepackage{amsmath}

@@

\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\vect}[1]{\mbox{\boldmath $#1$}}
\newcommand{\erf}{\mathrm{erf}}
\newcommand{\PS}{Pfirsch-Schl\"{u}ter~}
\newcommand{\ExB}{\vect{E}\times\vect{B}}
\newcommand{\Cnl}{C_{\mathrm{nl}a}}
\newcommand{\vma}{\vect{v}_{\mathrm{m}a}}
\newcommand{\vm}{\vect{v}_{\mathrm{m}}}
\newcommand{\vda}{\vect{v}_{\mathrm{d}a}}
\newcommand{\vE}{\vect{v}_{E}}
\newcommand{\vdao}{\vect{v}_{\mathrm{d}a0}}
\newcommand{\vdo}{\vect{v}_{\mathrm{d}0}}
\newcommand{\vEo}{\vect{v}_{E0}}
\newcommand{\vpar}{v_{||}}
\newcommand{\vperp}{v_{\bot}}
\newcommand{\rhop}{\rho_{\theta}}
\newcommand{\rT}{r_{T}}
\newcommand{\vi}{v_{\mathrm{i}}}
\newcommand{\me}{m_{\mathrm{e}}}
\newcommand{\mi}{m_{\mathrm{i}}}
\newcommand{\Ti}{T_{\mathrm{i}}}
\newcommand{\rTi}{r_{T\mathrm{i}}}
\newcommand{\rTe}{r_{T\mathrm{e}}}
\newcommand{\reta}{r_{\eta}}
\newcommand{\rn}{r_{n}}
\newcommand{\rperp}{r_\bot}
\newcommand{\fM}{f_{\mathrm{M}}}
\newcommand{\fMa}{f_{\mathrm{M}a}}
\newcommand{\fMi}{f_{\mathrm{M}i}}
\newcommand{\fMe}{f_{\mathrm{Me}}}
\newcommand{\fe}{f_{\mathrm{e}}}
\newcommand{\Te}{T_{\mathrm{e}}}
\newcommand{\vth}{v_{\mathrm{th}}}
\newcommand{\nuii}{\nu_{\mathrm{ii}}}
\newcommand{\nuPrime}{\hat{\nu}}
\newcommand{\gradpar}{\nabla_{||}}
\newcommand{\kpar}{k_{||}}
\newcommand{\psia}{\psi_0}
\newcommand{\psiaHat}{\hat{\psi}_0}
\newcommand{\todo}[1]{\textcolor{red}{To do: #1}}
\newcommand{\sgn}{\mathrm{sgn}}
\newcommand{\Erres}{E_r^{\mathrm{res}}}
\newcommand{\Bpol}{B_{\mathrm{pol}}}
\newcommand{\Sap}{S_{a\mathrm{p}}}
\newcommand{\Sah}{S_{a\mathrm{h}}}
%\newcommand{\changed}[1]{#1}
\newcommand{\changed}[1]{\textcolor{red}{#1}}

@@

\author{M Landreman}
\email[]{mattland@umd.edu}
%\homepage[]{Your web page}
%\thanks{}
\affiliation{Institute for Research in Electronics and Applied Physics, University of Maryland, College Park, MD, 20742, USA}
\author{H M Smith}
\affiliation{Max-Planck-Institut f\"{u}r Plasmaphysik, 17491 Greifswald, Germany}
\author{A Moll\'{e}n}
\affiliation{Department of Applied Physics, Nuclear Engineering,
  Chalmers University of Technology and Euratom-VR Association,
  G\"oteborg,
  Sweden}
\author{P Helander}
\affiliation{Max-Planck-Institut f\"{u}r Plasmaphysik, 17491 Greifswald, Germany}

@@

@@

\changed{
In the short-mean-free-path limit $\nu' \gg 1$, the ion transport and flow can be computed
analytically in terms of the parallel current \cite{AndreiPer2009}.
The transport matrix elements associated with the Fokker-Planck collision operator
may therefore be extracted from Ref. \cite{AndreiPer2009} and are summarized in Appendix \ref{apdx:SH}.
Plotted in figures \ref{fig:collisionComparison_LHD} and \ref{fig:collisionComparison_W7X} (red dashed lines),
these analytic high-collisionality limits agree quite well with the Fokker-Planck SFINCS computations
in the appropriate $\nu' \gg 1$ limit.
}

\changed{
At any collisionality, when the pure pitch-angle scattering collision operator 
and DKES trajectories are chosen, the kinetic equation
solved in SFINCS becomes identical to the one solved in the DKES code \cite{DKES1, DKES2}.
In this case, it was verified that the two codes agreed for all elements of the transport
matrix, as demonstrated in figure \ref{fig:collisionComparison_W7X}.
For this figure, the monoenergetic transport coefficients
computed by DKES have been integrated over velocity with the appropriate
weights and normalized in the same way as (\ref{eq:matrix}).
}

\begin{figure}[h!]
% Figure generated using m20140127_01_plotSFINCSFortranAndMatlabNuScansForPaper.m
% *********************************
% Previous version of figure generated using m20131208_01_plotSFINCSFortranAndMatlabNuScansForPaper.m
% High collisionality runs done in matlab, with data in
% m20130226_04_SFINCS_2013-02-26_21-21_good
% Low collisionality runs done in fortran on edison.
% *********************************
% Previous version of figure:
% Figure generated using m20131130_01_plotSFINCSCollisionOperatorComparisonForPaper.m
% Data files:
% m20131117_04_sfincs_w7x_2013-11-26_02-27_nuPrimeScan_nuPrime0_01to100
% m20130226_04_SFINCS_2013-02-26_21-21_good
% W7X run was on edison in /global/scratch2/sd/landrema/20131123-01-sfincs/20131125-02-nuPrimeScan0_01to100
% *********************************
\includegraphics{m20140127_01_plotSFINCSFortranAndMatlabNuScansForPaper_LHD.eps}
%\includegraphics{m20131208_01_plotSFINCSFortranAndMatlabNuScansForPaper_LHD.eps}
%\includegraphics{m20131130_01_plotSFINCSCollisionOperatorComparisonForPaper_LHD.eps}
\caption{(Color online) 
The ion transport matrix elements (defined in (\ref{eq:matrix})) are plotted as functions
of the collisionality (\ref{eq:nuPrime}) for LHD geometry at $E_r=0$.
SFINCS computations for three different collision operators are compared.
\changed{
Dashed red lines indicate the analytic high-collisionality limits
for Fokker-Planck collisions, discussed in appendix \ref{apdx:SH} and in Ref. \cite{AndreiPer2009},
which agree quite well with the SFINCS Fokker-Planck computations at high collisionality.
}
\label{fig:collisionComparison_LHD}}
\end{figure}

\begin{figure}[h!]
% Figure generated using m20140127_01_plotSFINCSFortranAndMatlabNuScansForPaper.m
% *********************************
% Previous version of figure generated using m20131208_01_plotSFINCSFortranAndMatlabNuScansForPaper.m
% High collisionality runs done in matlab, with data in
% m20131117_04_sfincs_w7x_2013-11-26_02-27_nuPrimeScan_nuPrime0_01to100
% Low collisionality runs done in fortran on edison.
% *********************************
% Previous version of figure:
% Figure generated using m20131130_01_plotSFINCSCollisionOperatorComparisonForPaper.m
% Data files:
% m20131117_04_sfincs_w7x_2013-11-26_02-27_nuPrimeScan_nuPrime0_01to100
% m20130226_04_SFINCS_2013-02-26_21-21_good
% W7X run was on edison in /global/scratch2/sd/landrema/20131123-01-sfincs/20131125-02-nuPrimeScan0_01to100
% *********************************
\includegraphics{m20140127_01_plotSFINCSFortranAndMatlabNuScansForPaper_W7X.eps}
%\includegraphics{m20131208_01_plotSFINCSFortranAndMatlabNuScansForPaper_W7X.eps}
%\includegraphics{m20131130_01_plotSFINCSCollisionOperatorComparisonForPaper_W7X.eps}
\caption{(Color online)
The ion transport matrix elements (defined in (\ref{eq:matrix})) are plotted as functions
of the collisionality (\ref{eq:nuPrime}) for LHD geometry at $E_r=0$.
SFINCS computations for three different collision operators are compared.
\changed{
Dashed red lines indicate the analytic high-collisionality limits
for Fokker-Planck collisions, discussed in appendix \ref{apdx:SH} and in Ref. \cite{AndreiPer2009},
which agree quite well with the SFINCS Fokker-Planck computations at high collisionality.
Also shown (black crosses) are the transport matrix elements
computed using the DKES code \cite{DKES1,DKES2}, which uses a pitch-angle scattering collision operator,
demonstrating excellent agreement with SFINCS when the latter is run with the same collision model. 
}
\label{fig:collisionComparison_W7X}}
\end{figure}

@@

\section{Ion transport matrix at high collisionality}
\label{apdx:SH}

\changed{
From the analytic calculations presented in Ref.~\cite{AndreiPer2009} we can derive expressions
for $L_{jk}$ of Eq.~(\ref{eq:matrix}) in the Pfirsch-Schl{\"u}ter regime. 
The transport matrix elements then depend on the function $u$ given by the solution to Eq.~(8) in Ref.~\cite{AndreiPer2009};
$u$ is proportional to the parallel current divided by $B$. 
All coefficients but $L_{33}$ are straightforwardly obtained from Eqs.~(14), (18) and (26) in Ref.~\cite{AndreiPer2009} for the radial ion heat flux, the parallel ion flow, and the radial current respectively, by %properly choosing 
suitable choices of 
the thermodynamic forces in the right-hand-side of Eq.~(\ref{eq:matrix}) and using the symmetry of the transport matrix.
To find the parallel conductivity coefficient $L_{33}$ we substitute the pressure anisotropy, given by Eq.~(20) in Ref.~\cite{AndreiPer2009}, into Eq.~(\ref{ParallelMomentum}) (of this paper) 
in the absence of radial gradients (i.e. when $E_{||}$ is the only thermodynamic force present). Then $L_{33}$ can be found from the flow $\left< V_\| B \right>$.
}

\changed{
Expressions for the matrix coefficients in the Pfirsch-Schl{\"u}ter regime are summarized in 
Eqs.~(\ref{eq:LPSregime})-(\ref{eq:PSregimeFunctions}). 
Three numerical coefficients in the function ${K}_2^{\mathrm{Simakov}} \left(\psi\right)$
arise from generalized Spitzer problems, 
which were solved in Ref.~\cite{AndreiPer2009} by keeping a small number of Laguerre polynomials in kinetic energy.
When these generalized Spitzer problems are solved numerically keeping many more energy polynomials,
we obtain the more accurate coefficients given in ${K}_{2}$ below.
}

\changed{
%\begin{equation}
%\begin{array}{c}
\begin{align}
\begin{split}
L_{11} & = 
 0.96 \cdot 2^{1/2} \cdot  \frac{3}{4}  \frac{\left(G + \iota I\right)^2}{ \iota^2 G^2} 
 {G}_1 \left(\psi\right) \frac{1}{\nu'},\\
 %%
L_{12} & = L_{21} =  0.96 \cdot 2^{1/2} \frac{\left({G} + \iota {I}\right)^2}{ \iota^2 {G}^2} \left[ 3.245 \, {G}_1 \left(\psi\right) + 0.085 \, {G}_2 \left(\psi\right)  \right] \frac{1}{\nu'}, \\
%% 
L_{13} & = L_{31}  = \frac{\left\langle {u} {B}^2  \right\rangle}{{G} \iota} - \frac{\left\langle {B}^2\right\rangle}{{G} \iota} {K}_1\left(\psi\right), \\
%%
L_{22} & = 2^{1/2} \cdot  \frac{8}{5} \frac{1}{\iota^2 {G}^2} B_0^2 {H} \left(\psi\right) \, \nu', \\
	%\textcolor{red}{+ \left( \,0.96 \cdot 2^{1/2} \cdot \frac{5}{2} \frac{\left({G} + \iota {I}\right)^2}{ \iota^2 {G}^2} \left[ 3.245 {G}_1 \left(\psi\right) + 0.085 {G}_2 \left(\psi\right)  \right] \frac{1}{\nu'}\right)}, \\
	%%
L_{23} & = L_{32} = \frac{1}{\iota {G}} \left[\frac{5}{2} \left\langle {u} {B}^2  \right\rangle - \frac{5}{2} {K}_1\left(\psi\right) \left\langle {B}^2\right\rangle + {K}_2\left(\psi\right) \left\langle {B}^2\right\rangle\right], \\
%%
L_{33} & = \frac{1}{3 \cdot 0.96 \cdot 2^{1/2}} \frac{1}{\left({G} + \iota {I}\right)^2} \frac{\left\langle {B}^2\right\rangle^2}{\left\langle \left( {\nabla}_\| {B}\right)^2\right\rangle} \, \nu',	
%\end{array}
\label{eq:LPSregime}
\end{split}
\end{align}
%\end{equation}
%where
\begin{align}
\begin{split}
& {G}_1 \left(\psi\right) %& 
= \frac{\left\langle \left( {\nabla}_\| \ln {B}\right)  {\nabla}_\| \left({u} {B}^2\right)\right\rangle^2}{\left\langle \left( {\nabla}_\| {B}\right)^2\right\rangle} -
 \left\langle \left[\frac{ {\nabla}_\| \left({u} {B}^2\right)}{{B}}\right]^2\right\rangle,  \\
 %%
& {G}_2 \left(\psi\right) %& 
 = \left\langle {u} \left({\nabla}_\| \ln {B}\right) {\nabla}_\| \left({u} {B}^2\right) \right\rangle
 - \frac{\left\langle \left( {\nabla}_\| \ln {B}\right)  {\nabla}_\| \left({u} {B}^2\right)\right\rangle
 \left\langle {u} \left( {\nabla}_\| {B}\right)^2\right\rangle}{\left\langle \left( {\nabla}_\| {B}\right)^2\right\rangle},  \\
 %%
& {K}_1 \left(\psi\right) %& 
 = \frac{\left\langle \left( {\nabla}_\| \ln {B}\right)  {\nabla}_\| \left({u} {B}^2\right)\right\rangle}{2 \left\langle \left( {\nabla}_\| {B}\right)^2\right\rangle}, \\
 %%
& {K}_2 \left(\psi\right) %& 
 = 1.97213 \frac{\left\langle {u} {B}^2  \right\rangle}{\left\langle {B}^2  \right\rangle} - 1.03287 \cdot 2 {K}_1 \left(\psi\right)
 + 0.09361 \frac{
 \left\langle {u} \left( {\nabla}_\| {B}\right)^2\right\rangle}{\left\langle \left( {\nabla}_\| {B}\right)^2\right\rangle}, \\
 %%
&  {K}_{2}^{\mathrm{Simakov}} \left(\psi\right) %& 
  = 1.77 \frac{\left\langle {u} {B}^2  \right\rangle}{\left\langle {B}^2  \right\rangle} - 0.91 \cdot 2 {K}_1 \left(\psi\right)
 + 0.05 \frac{
 \left\langle {u} \left( {\nabla}_\| {B}\right)^2\right\rangle}{\left\langle \left( {\nabla}_\| {B}\right)^2\right\rangle}, \\
 %%
& {H} \left(\psi\right) %& 
 = \frac{\left\langle {u} {B}^2  \right\rangle^2}{\left\langle {B}^2  \right\rangle} - \left\langle {u}^2 {B}^2  \right\rangle.
\label{eq:PSregimeFunctions}
\end{split}
\end{align}
}
